---
title: 'Problem Set 4: Randomized Control Trials'
author: "Claire Duquennois"
output:
 html_document:
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Name: Yanhao Quan (Barney)**

Instructions: 

- This assignment is an individual assignment. You may discuss your responses in small groups or reach out to a classmate if you are having difficulties with coding but your code and answers must reflect your individual efforts and be written using your own words. Identical assignments will be given a zero grade. 

- You must post your code in a private repo on GitHub and invite the TA and I as collaborators. 

- You must update your work on GitHub frequently through commits where we can observe which lines you most recently worked on when we click on the repo history. This is done very easily if you are using Git correctly which is part of what we are assessing with this assignment. Make sure you make at least five commits that highlight your most recent changes. 




# Empirical Analysis using Data from Bryan, G., Chowdury, S., Mobarak, A. M. (2014, Econometrica)


This exercise uses data from Bryan,Chowdhury, and Mobarak's paper, "Underinvestment in a Profitable Technology: the Case of Seasonal Migration in Bangladesh," published in *Econometrica* in 2014. This paper studies the effects of seasonal migration on household consumption during the lean season in rural Bangladesh by randomly subsidizing the cost of seasonal migration. 


# Set Up: 

## Finding the data

The data can be found by going to Mushfiq Mobarak's Yale faculty page, select "data", and then following the link to the data repository page on the Harvard dataverse. You will need to sign in to get access to the data files. Once logged in, you will find many possible files to download. Navigate to the second page of listed files and download `Mobarak - Monga Dataverse files.zip` which contains all the files we need. 

```{r}
library(haven)
library(dplyr)
library(stargazer)
library(lfe)

```



## Question: Loading the data - Load any packages you will need and the data contained in the following files `Round1_Controls_Table1.dta` and `Round2.dta`. How many observations are contained in each of these datasets. What is the level of an observation? Explain any discrepancies between the datasets.**

**Code:**
```{r}
#Loading the data
rct1 <- read_dta("C:/Users/85384/Desktop/PS4/Mobarak-Monga_Dataverse_files/Data/Round1_Controls_Table1.dta")
rct1<-as.data.frame(rct1)
View(rct1)
r2 <- read_dta("C:/Users/85384/Desktop/PS4/Mobarak-Monga_Dataverse_files/Data/Round2.dta")
r2<-as.data.frame(r2)
View(r2)

```

```{r}
nrow(rct1)
ncol(rct1)
```

```{r}
nrow(r2)
ncol(r2)
```

**Answer:**
The Round1_Controls_Table1 data contains 1900 observations where each observations is for one village. And the Round2 data contains 1907 observations for one village. And Round2 has follow up data about the migration experience, contained more variables, and I will say Round2's data are build upon Round1"s.

 
## Question: Data Description- The dataset contains many variables, some of which are not used in this exercise. Keep the following variables in the final datasets (Hint: use the `select` function in `dplyr`).** 

For Round 1 data:

| Name            |Description                                                             |
|-----------------|------------------------------------------------------------------------|
|cash             |In cash treatment group                                                 |
|credit           |In credit treatment group                                               |
|info             |In information treatment group                                          |
|control          |In control group                                                        |
|q9pdcalq9        |Total calories per person per day                                       | 
|exp_total_pc_r1  |Total monthly household expenditures per capita                         |
|hhmembers_r1     |Number of household members                                             |
|tsaving_hh_r1    |Total household savings                                                 |
|hhh_education    |Household head is educated                                              |
|num_adltmalesr1  |Number of adult males in the household                                  |

For Round 2 data:

| Name          |Description                                                             |
|---------------|------------------------------------------------------------------------|
|cash           |In cash treatment group                                                 |
|credit         |In credit treatment group                                               |
|info           |In information treatment group                                          |
|control        |In control group                                                        |
|average_exp2   |Total consumption per person per month in round 2                       |
|lit            |Highest reading and writing ability of household                        |
|walls_good     |Wall material (income proxy)                                            |
|monga          |Subjective expectations about monga at baseline                         |
|dhaka_remit    |Subjective expectations about migration remitances at baseline          |
|dhaka_network  |Subjective expectations about social network in city at baseline        |
|exp_total_pc_r1|Total household expenditures per capita at baseline                     |
|subsistencer1  |Share of food out of total expenditures at baseline                     |
|num_adltmalesr1|Household adult males at baseline                                       |
|num_childrenr1 |Household small children at baseline                                    |
|avgQ13earned   |Average skill score of network                                          |
|constrainedr1  |Denied or ineligible for credit at baseline                             |
|bankedr1       |Has received credit at baseline                                         |
|upazila        |Sub-district name                                                       |
|village        |Village name                                                            |
|migrant        |Member of household migrates this season                                |
|total_fish     |Total monthly household expenditures per capita on fish                 |
|migrant_new    |Household has a first time migrant this season                          |



**A description of each variable should appear in the column headers of the loaded data. **

**Code:**
```{r}
#select the data from the original data set
rct1 <- as.data.frame(rct1)
selected_rct1 <- select(rct1, cash, credit, info, control, q9pdcalq9, exp_total_pc_r1, hhmembers_r1, tsaving_hh_r1, hhh_education, num_adltmalesr1)
selected_rct1 <- as.data.frame(selected_rct1)
```


```{r}
#select the data from the original data set
r2 <- as.data.frame(r2)
selected_r2 <- select(r2, cash, credit, info, control, average_exp2, lit, walls_good, monga, dhaka_remit, dhaka_network, exp_total_pc_r1, subsistencer1, num_adltmalesr1, num_childrenr1, avgQ13earned, constrainedr1, bankedr1, upazila, village, migrant, total_fish, migrant_new)
selected_r2 <- as.data.frame(selected_r2)
```


# Analysis:

## **Question: Regress all the baseline household characteristics still included in the round 1 data on the following three variables: $cash_i$, $credit_i$ and $info_i$, and present your results in a table. What is the equivalent table in the paper?** 

**Code:**
```{r}
reg1 <- felm(selected_rct1$q9pdcalq9 ~ selected_rct1$cash + selected_rct1$credit + selected_rct1$info)

reg2 <- felm(selected_rct1$exp_total_pc_r1 ~ selected_rct1$cash + selected_rct1$credit + selected_rct1$info)

reg3 <- felm(selected_rct1$hhmembers_r1 ~ selected_rct1$cash + selected_rct1$credit + selected_rct1$info)

reg4 <- felm(selected_rct1$tsaving_hh_r1 ~ selected_rct1$cash + selected_rct1$credit + selected_rct1$info)

reg5 <- felm(selected_rct1$hhh_education ~ selected_rct1$cash + selected_rct1$credit + selected_rct1$info)

reg6 <- felm(selected_rct1$num_adltmalesr1 ~ selected_rct1$cash + selected_rct1$credit + selected_rct1$info)

```

```{r echo=FALSE, resize.width=10, results='asis'}
stargazer(reg1, reg2, reg3, reg4, reg5, reg6, type = "html", dep.var.caption = "RANDOMIZATION BALANCE ON OBSERVABLES AT BASELINE", dep.var.labels = c("Total calories per person per day", "Total monthly household expenditures per capita", "Number of household members", "Total household savings", "Household head is educated", "Number of adult males in the household"), covariate.labels = c("In cash treatment group", "In credit treatment group", "In information treatment group"), notes.label = "Significance Levels")

```

**Answer:** Table 1 is the equivalent one in this paper.


## **Question: How should the coefficients in the table above be interpreted? What should we look for in this table?**

**Answer:** The estimators in the table above are basically not significant, which is a good thing because all baseline household characteristics we don't want them have correlation with our treatment variables. In this case our treatments are all good treatments. 


## **Question: Using the round 2 data, regress migrant on the treatment arm indicators. What is the equivalent table in the paper?**

**Code:**
```{r echo=FALSE, resize.width=10, results='asis'}
reg7 <- felm(selected_r2$migrant ~ selected_r2$cash + selected_r2$credit + selected_r2$info)
reg8 <- felm(selected_r2$migrant_new ~ selected_r2$cash + selected_r2$credit + selected_r2$info)

stargazer(reg7, reg8, type = "html", dep.var.caption = "PROGRAM TAKE-UP RATES", dep.var.labels = c("Member of household migrates this season", "Household has a first time migrant this season"), covariate.labels = c("Cash", "Credit", "Info"), notes.label = "Significance Levels")
```


**Answer:** Table 2 is the equivalent table in the paper.


## **Question: How should the coefficients in the table above be interpreted? Why is this table important?**

**Answer:** The estimators of cash treatment and credit treatment are significant but Info treatment is not, then it is important because we could tell the relationship between migrant and cash and credit. We could say under cash treatment, the member of household migrates this season increased 23% and vice versa.


## **Question: What is the underlying migration rate in the control group and how might this change our interpretation of the results? **

**Answer:**The underlying migration rate in the control group is 36%, this mean when the migration rate under cash and credit treatment will increase 23% and 20.8% more compares to th control group.


## **Question: Replicate the results presented in the third row of the first three columns of table 3. Present them in a table and interpret these results. **

Note 1: The authors elect to drop one household observation because the reported value of total fish consumed in the household is very high. 

Note 2: To replicate the standard errors in the paper you will need to cluster your standard errors at the village level. We will discuss clustering later in the semester.  Using `felm` you can specify the level of clustering (`clustervariable`) using the following command:

`reg<-felm(Y~x1|fevariables|(ivfirststage)|clustervariable, dataname)` 

where you can replace fevariables and ivfirststage with 0 if you are not using fixed effects or an instrument. 


**Code:**
```{r echo=FALSE, resize.width=10, results='asis'}
reg8 <- felm(selected_r2$average_exp2 ~ selected_r2$cash + selected_r2$credit + selected_r2$info |upazila|0|village, selected_r2)
stargazer(reg8, type = "html", dep.var.caption = "EFFECTS OF MIGRATION ON CONSUMPTION AMONGST REMAINING HOUSEHOLD MEMBERS", dep.var.labels = c("Total consumption"), covariate.labels = c("Cash", "Credit", "Info"), notes.label = "Significance Levels")

```


**Answer:** The result shown above is quite close to the result presented in the paper.


## **Question: What happens to these estimates if you drop the fixed effects from the specification. Why? **

**Code:**
```{r echo=FALSE, resize.width=10, results='asis'}
reg9 <- felm(selected_r2$average_exp2 ~ selected_r2$cash + selected_r2$credit + selected_r2$info |0|0|village, selected_r2)
stargazer(reg9, type = "html", dep.var.caption = "EFFECTS OF MIGRATION ON CONSUMPTION AMONGST REMAINING HOUSEHOLD MEMBERS", dep.var.labels = c("Total consumption"), covariate.labels = c("Cash", "Credit", "Info"), notes.label = "Significance Levels")
```



**Answer:**Compare to with the fixed effect, the estimator for credit become non-significant, and the estimator of cash dropped a little bit. This could explained by there is a relationship between the a certain sub-district name and cash and credit. Therefore when we remove the fixed effect, it effect our regression and make it less accurate.




## **Question: Replicate the results presented in the third row of the fourth and fifth columns of table 3. What happens to the coefficient and standard errors? Is this surprising? What does this tell us?**

Hint: You will need to construct a new variable to run these estimates. 


**Code:**
```{r}
r2$treat <- ifelse(r2$cash == '1' | r2$credit == '1', 1, 0) 
```

```{r}
reg10 <- felm(r2$average_exp2 ~ r2$treat|upazila|0|village, data = r2)
reg11 <- felm(r2$average_exp2 ~ r2$treat + walls_good + subsistencer1 + num_adltmalesr1 + num_childrenr1 + constrainedr1 + bankedr1 + exp_total_pc_r1 + monga + dhaka_network|upazila|0|village, r2)

```
#I'm not sure why the result below is different from that in paper
```{r echo=FALSE, resize.width=10, results='asis'}
stargazer(reg10, reg11, type = "html", style = "qje", title = "EFFECTS OF MIGRATION ON CONSUMPTION AMONGST REMAINING HOUSEHOLD MEMBERS", dep.var.caption = "Intent-to-Treat", dep.var.labels = c("ITT", "ITT"), covariate.labels = c("Total consumption","Wall material (income proxy)", "percentage of total expenditure on food", "number of adult males", "number of children", "lacked access to credit", "borrowing", "total household expenditures per capita measured at baseline", "subjective expectations about monga", "social network support measured at baseline"), notes.label = "Significance Levels")
```



**Answer:**
The coefficients dropped and standard error increased and become less coefficient, and it is not suprising because we are not put any instrumental variable into the regresion function right now.

## **Question: Why is the header of the first five columns of table 3 "ITT". What is meant by this and what does this tell us about how we should interpret these results?**

**Answer:** "ITT" means intent-to-treat, the regression model is to present pure experimental (intent-to-treat) estimate, with consumption measures regressed on randomly assigned treatment: cash,credit, and information for migration. You could think ITT as a dummy variable for either get treated or not treated. Column 4 reports the intent-to-treat estimates for these two incentive treatments jointly, and column 5 indicates that these effects are generally robust to adding some controls for baseline characteristics. So the first five columns of table 3 are "ITT". We could interpret it as after cash treatment, the total consumption increases 97 Taka per household member per month, after credit treatment, the total consumption increases 77 Taka per household member per month, and in overall, the treatmet group increases the consumption by 61 Taka per household member per month.

## **Question: We are interested in estimating how migration affects total expenditures for the households that were induced to migrate by the cash and credit treatments as follows,**

$$
TotExp_{ivj}=\alpha+\beta_1Migrate_{ivj}+\theta X_{ivj}+\varphi_j+\nu_{ivj}
$$
**where $Migrate_{ivj}$ is dummy indicator for if a member of household i in village v in subdistrict j migrated, $X_{ivj}$ is a vector of control variables and $\varphi_j$ are the subdistrict fixed effects. However it is not possible to identify in the data which households were induced by the treatment vs those who would have migrated either way. Furthermore, there is likely substantial selection between the households that select into migration versus those that do not. Propose a source of exogenous variation that can be used as an instrument to isolate "good" exogenous variation in migration. **

**Answer:** 
 

## **Question: What is the first stage specification?**

**Answer:** use cash and credit as the treatment and effect the total consumption by giving treatment on new migration, since cash and credit could increase new migration, therefore total consumption would increase due to migration increases.


## **Question: Estimate the first stage and check that you have a strong instrument for migration.**

 Note: The first stage results reported in the paper appendix may differ slightly as explained in the table footnote.  

**Code:**
```{r}
reg12 <- felm(data = selected_r2, migrant_new ~ selected_r2$cash + selected_r2$credit)
summary(reg12)
```



**Answer:** the t value are all quite big, and the p-value are so small means it is significant, then we have a strong instrument for migration.


## **Question: Use your instrument to estimate the LATE (Local Average Treatment Effect), the impact of migration on total consumption for those induced to migrate by the treatment, as in columns 6 and 7 of table 3 in the paper. Interpret your results. **

Note: if you wish to replicate the paper's coefficients exactly, you will need to use multiple instruments, one for each treatment arm.

**Code:**
```{r}
reg13 <- felm(r2$average_exp2 ~ 1 |upazila | (migrant_new ~ cash + credit) | village, r2)
reg14 <- felm(r2$average_exp2 ~ lit + walls_good + subsistencer1 + num_adltmalesr1 + num_childrenr1 + constrainedr1 + bankedr1 + exp_total_pc_r1 + monga + dhaka_remit + dhaka_network + avgQ13earned | upazila | (migrant_new ~ cash + credit) | village, r2)
```

```{r echo=FALSE, resize.width=10, results='asis'}
stargazer(reg13, reg14,
          type= "html",
          style = "qje",
          title= "LATE of Migration on Total Consumption",
          omit = c("lit", "walls_good", "subsistencer1", "num_adltmalesr1", "num_childrenr1", "constrainedr1", "bankedr1", "exp_total_pc_r1", "monga", "dhaka_remit", "dhaka_network", "avgQ13earned"),
          dep.var.caption = c("Total consumption"),
          dep.var.labels = c("Total consumption", "Total consumption"),
          covariate.labels = c("IV"), 
          notes.label = "Significance Levels",
          add.lines = list(c("controls", "No", "Yes")))

```


**Answer:**The table above shows the Local Average Treatment Effect of Migration on Total Consumption. (1) is the estimator with IV first stage and without any controls, the total consumption will increase about 353 Taka per household member per month. If we do the regression with all those controls above, the total consumption will increase about 312 Taka per household member per month. All the estimators above are significant.



## **Question: Why are these results different from those in columns 4 and 5 of the paper?  **

**Answer:** because for column 4 and 5, we are not using any instrumental variable, so there will be many omitted variables, that is why the results are different.


## **Question: Why is this value particularly relevant for policy decisions in the context of this experiment.**

**Answer:** because we could tell from the regression function if we decide to use this policy, will it bring us the positive results. The table above shows us the real effect on implement this policy. The results are all significant means we could use this policy in a small scale.


## **Question: Suppose a policy maker found these results so compelling that they decided to make this a national policy. How would general equilibrium effects potentially change the impacts of this policy if it was implemented in a very large scale way?**

**Answer:**If the policy were implemented at scale, some interventions could affect national level variables which in turn could potentially counteract some of the benefits that were estimated in the small scale experiment.


## **Question: One major concern that is often brought up in discussions about RCT's is the problem of external validity. It is not always clear how informative the findings from a small scale research project in one context are for policy makers working on a different scale and in different contexts. What are your thoughts on the external validity of this particular project and RCT's in general? **

**Answer:** In general, RCT’s (especially in development economics) are often conducted in a limited geographical area with a relatively small sample size. (Small as compared to the kind of sample you might have when working with large administrative data.) It is thus not always clear if you would expect to get the same results in a different context or if the program were implemented on a larger scale. Because RCT’s are often implemented with a lot more care and resources then a large scale policy might be, it is also not clear if we would expect the same results. 

In this particular project, the quantitative work implies that we are not be able to provide a fully satisfying explanation for why people in Rangpur had not saved up to migrate. We are therefore hesitant to draw policy implications from our research. However, it is clear that the migration support programs we implement help some Rangpur households cope with the monga famine, and appear more cost-effective than subsidizing food purchases on an ongoing basis, which is the major anti-famine policy tool currently employed by the Bangladesh government.

# Submission instructions:

1) Make sure the final version of your assignment is uploaded on GitHub in both html and Rmarkdown format. 




